---
title: "ADVTTEST"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ADVTTEST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The package `ADVTTEST` can be used to do Hypothesis Testing using a T-Test to decide if the population means of two samples are identical or not. This package will run a T-Test on paired samples, unpaired samples, and samples with equivalent and unequal variances.

## Package Installation 

The below are the steps to install the package `ADVTTEST`

1. Install project [R](https://cran.r-project.org "R")

2. Install [R Studio](https://www.rstudio.com/products/rstudio/download/, "R Studio") 

3. Open R Studio and install `devtools` using command 
`install.packages("devtools")`

4. Install the package `ADVTTEST` using command 
`devtools::install_github('https://github.com/Harikiran-Madishetti/T-Test.git', auth_token = <token>)`

## Package Functions

This package as the below functions:

1. `myttest` a constructor function

2. `plot.Rttest` a generic plot function for class `Rttest`

3. `print.Rttest` a generic print function for class `Rttest`

4. `shinyttest` a function used to run reactive shiny web application


```{r setup}
library(ADVTTEST)
```

# Testing Package

## Non Paired Salples with Eqlal Variances
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y=rnorm(30,mean=8,sd=15)
ans1=ADVTTEST::myttest(x,y,alpha=0.05,paired=FALSE)
```

```{r}
print(ans1)
```
```{r}
plot(ans1)
```

## Non Paired Salples with Uneqlal Variances
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=5)
set.seed(35); y=rnorm(30,mean=8,sd=15)
ans2=ADVTTEST::myttest(x,y,alpha=0.05,paired=FALSE)
```

```{r}
print(ans2)
```

```{r}
plot(ans2)
```

## Paired Salples
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y = x+ rnorm(30, 5 ,4)
ans3=ADVTTEST::myttest(x,y,alpha=0.05,paired=TRUE)
```

```{r}
print(ans3)
```

```{r}
plot(ans3)
```
