---
title: "ADVTTEST"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ADVTTEST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The package `ADVTTEST` can be used to do Hypothesis Testing using a T-Test to decide if the population means of two samples are identical or not. This package will run a T-Test on paired samples, unpaired samples, and samples with equivalent and unequal variances.

## Package Installation 

The below are the steps to install the package `ADVTTEST`

1. Install project [R](https://cran.r-project.org "R")

2. Install [R Studio](https://www.rstudio.com/products/rstudio/download/, "R Studio") 

3. Open R Studio and install `devtools` using command 
`install.packages("devtools")`

4. Install the package `ADVTTEST` using command 
`devtools::install_github('https://github.com/m-harikiran/T-Test.git', auth_token = <token>, build_vignettes = TRUE)`

## Package Functions

This package as the below functions:

1. `myttest` a constructor function

2. `plot.Rttest` a generic plot function for class `Rttest`

3. `print.Rttest` a generic print function for class `Rttest`

4. `shinyttest` a function used to run reactive shiny web application

### Constructor 

The constructor function is called `myttest`, and it takes four input samples as vectors, a logical variable (default FALSE) and a numeric variable (default 0.05). Performs hypothesis testing, returning a list of class `Rttest` objects containing the test type, test summary, hypothesis test conclusion, and input sample data.
```{r, eval=FALSE, include=TRUE}
# Checking if the given input vectors are paired or not
if (paired == FALSE)
{
  #If the given samples are not paired then
  #Perform F-Test to know the variability of the samples
  
  ftest <- var.test(x, y)
  #alternative hypothesis: true ratio of variances is not equal to 1
  #If p-value is > alpha or significance level we fail to reject null
  
  if (ftest$p.value > alpha) {
    #Equal variance
    testType <- 'T-TEST'
    
    ttest <-
      t.test(x, y, var.equal = TRUE, conf.level = 1 - alpha)
    
    if (ttest$p.value > alpha) {
      conclusion <- 'N'
    } else {
      conclusion <- 'Y'
    }
  }
  else {
    #Unequal Variance
    testType <- 'WELCH'
    
    ttest <-
      t.test(x, y, var.equal = FALSE, conf.level = 1 - alpha)
    
    if (ttest$p.value > alpha) {
      conclusion <- 'N'
    } else {
      conclusion <- 'Y'
    }
  }
  
}
else{
  #Given samples are paired
  testType <- 'PAIRED'
  
  if (length(x) != length(y))
    stop('For Paired Samples Length of X and Y must be same')
  
  ttest <- t.test(x, y, paired = TRUE, conf.level = 1 - alpha)
  
  if (ttest$p.value > alpha) {
    conclusion <- 'N'
  } else {
    conclusion <- 'Y'
  }
}

#List containing the results
lst = list(
  'Test_Type' = testType,
  'Test_Conclusion' = conclusion,
  'Test_Summary' = ttest,
  'Data' = inputDF
)
```

### Print Generic

The method `print.Rttest` is a generic print method for class `Rttest`. This method takes a class object as an input and prints confidence interval with confidence level and `Y` or `N` conclusion to reject NULL hypothesis.

```{r, eval=FALSE, include=TRUE}
print.Rttest <- function(x, ...) {
  if (!is.list(x))
    stop('The input is not a list')
  if (class(x) != 'Rttest')
    stop('The given input is not an object of class Rttest')
  
  ci <-
    x$Test_Summary$conf.int   #Accessing the confidence interval from test summary
  
  type <- x$Test_Type
  
  lst = list('Confidence Interval' = ci, 'Test Type' = type)
  
  print(lst)
}
```

### Plot Generic

The method `plot.Rttest` is a generic plot method for class `Rttest`. This method takes a class object as an input and plots box plot for unpaired data and box plot of differences if data is paired .

```{r, eval=FALSE, include=TRUE}
#Box Plot for Non-Paired samples
df = x$Data
gplot <-
  ggplot(df,
         aes(x = Variable,
             y = Data,
             fill = Variable)) + geom_boxplot(outlier.colour = "blue",
                                              outlier.size = 2) + labs(title = "Box Plot for unpaired samples",
                                                                       x = "Sample",
                                                                       y = "Values",
                                                                       fill = "Sample") + theme_bw()

#Box Plot for PAIRED Samples
df <-
  data.frame('data' = xValues - yValues, Variable = 'x') #Difference between x and y

gplot <-
  ggplot(df,
         aes(x = Variable,
             y = data)) + geom_boxplot(outlier.color = 'red', outlier.size = 2) + labs(title = "Box Plot for difference between paired samples", x = "Difference", y = "Values(x-y)") +   geom_errorbar(aes(
               ymin  = x$Test_Summary$conf.int[1],
               ymax  = x$Test_Summary$conf.int[2],
               width = 0.01
             )) + theme_bw()

```

### Shinyttest Method

The method `shinyttest` is used to run shiny web application, which can be used to interact with `ADVTTEST` package in an interactive way. This application displays the input samples data, summary of Hypothesis Testing and box plot's for paired and unpaired samples.

```{r, eval=FALSE, include=TRUE}
#The code to run the shiny application
shiny::runApp(system.file("ttest", package = "ADVTTEST"), launch.browser = TRUE)
```

## Shiny Application

This is a web application which can be used to interact with `ADVTTEST` package in an interactive way. The application can display the samples data, test statistics and box plots in a reactive way. The shiny application has two main components or functions UI and SERVER. In ui method all the components related to ui are defined and in server method all the back end functions are defined. The application can be opened using the command `ADVTTEST::shinyttest()`


## Testing Package

```{r setup}
library(ADVTTEST)
```

### Non Paired Salples with Eqlal Variances
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y=rnorm(30,mean=8,sd=15)
ans1=ADVTTEST::myttest(x,y,alpha=0.05,paired=FALSE)
```

```{r}
print(ans1)
```
```{r}
plot(ans1)
```

### Non Paired Salples with Uneqlal Variances
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=5)
set.seed(35); y=rnorm(30,mean=8,sd=15)
ans2=ADVTTEST::myttest(x,y,alpha=0.05,paired=FALSE)
```

```{r}
print(ans2)
```

```{r}
plot(ans2)
```

### Paired Salples
```{r}
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y = x+ rnorm(30, 5 ,4)
ans3=ADVTTEST::myttest(x,y,alpha=0.05,paired=TRUE)
```

```{r}
print(ans3)
```

```{r}
plot(ans3)
```
